### 2024-03-30 content/chapter_3.tex
:triangular_flag_on_post: Initial submission 240330

		\begin{remark}\label{re:reflection_coefficient}
			Since the reactance $X_l$ is a function of frequency, the reflection coefficient $\theta_l$ cannot be designed independently at different subbands. In this chapter, we assume the bandwidth is small compared to the operating frequency, such that the reflection coefficient at different subbands is approximately the same.
		\end{remark}

@@

		\begin{remark}\label{re:subband_tradeoff}
			The cascaded channel $\mathbf{V}_{n}$ varies at different subbands and there exists a trade-off for passive beamforming design in the frequency domain.
			Therefore, the equivalent subchannels should be carefully designed to meet specific requirements of multi-carrier \gls{swipt}. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\theta},n} \lVert \mathbf{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\theta}} \min_n \lVert \mathbf{h}_n \rVert$). That is to say, \gls{ris} enables a flexible subchannel design in multi-carrier transmissions. A similar effect also exists in the spatial domain for multi-antenna scenarios. In total, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
		\end{remark}
	\end{subsection}

@@

			Figs.~\subref*{fg:re_irs_1mhz} and \subref*{fg:re_irs_10mhz} explore the \gls{r-e} region with different \gls{ris} strategies for narrowband and broadband \gls{swipt}. The ideal \gls{fs} \gls{ris} assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive \gls{ris} adjusts the passive beamforming for different \gls{r-e} points by Algorithm~\ref{al:sca}. The \gls{wit}/\gls{wpt}-optimized \gls{ris} is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole \gls{r-e} region. The random \gls{ris} models the phase shift of all elements as i.i.d. uniform random variables over $[0, 2\pi)$. First, random \gls{ris} and no \gls{ris} perform worse than other schemes since no passive beamforming is exploited. Their \gls{r-e} boundaries coincide as the antenna mode reflection of the random \gls{ris} is canceled out after averaging. Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal \gls{fs} \gls{ris}. In the former case, the subband responses are close to each other such that the trade-off in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands. It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding equivalent channel and active precoder are also optimal for the whole \gls{r-e} region. Hence, the achievable \gls{r-e} region is obtained by optimizing the waveform amplitude and splitting ratio. On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal \gls{ris} reflection coefficient varies at different \gls{r-e} trade-offs points for broadband \gls{swipt}. As shown in Fig.~\ref{fg:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high \gls{snr}, or focused on a few strongest subbands to boost the output \gls{dc}, thanks to adaptive passive beamforming.
		\end{subsubsection}

>>>>

		\begin{remark}\label{rm:reflection_coefficient}
			Since the reactance $X_l$ is a function of frequency, the reflection coefficient $\theta_l$ cannot be designed independently at different subbands. In this chapter, we assume the bandwidth is small compared to the operating frequency, such that the reflection coefficient at different subbands is approximately the same.
		\end{remark}

@@

		\begin{remark}\label{rm:subband_tradeoff}
			The cascaded channel $\mathbf{V}_{n}$ varies at different subbands and there exists a trade-off for passive beamforming design in the frequency domain.
			Therefore, the equivalent subchannels should be carefully designed to meet specific requirements of multi-carrier \gls{swipt}. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\theta},n} \lVert \mathbf{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\theta}} \min_n \lVert \mathbf{h}_n \rVert$). That is to say, \gls{ris} enables a flexible subchannel design in multi-carrier transmissions. A similar effect also exists in the spatial domain for multi-antenna scenarios. In total, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
		\end{remark}
	\end{subsection}

@@

			Figs.~\subref*{fg:re_irs_1mhz} and \subref*{fg:re_irs_10mhz} explore the \gls{r-e} region with different \gls{ris} strategies for narrowband and broadband \gls{swipt}. The ideal \gls{fs} \gls{ris} assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive \gls{ris} adjusts the passive beamforming for different \gls{r-e} points by Algorithm~\ref{al:sca}. The \gls{wit}/\gls{wpt}-optimized \gls{ris} is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole \gls{r-e} region. The random \gls{ris} models the phase shift of all elements as i.i.d. uniform random variables over $[0, 2\pi)$. First, random \gls{ris} and no \gls{ris} perform worse than other schemes since no passive beamforming is exploited. Their \gls{r-e} boundaries coincide as the antenna mode reflection of the random \gls{ris} is canceled out after averaging. Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal \gls{fs} \gls{ris}. In the former case, the subband responses are close to each other such that the trade-off in Remark~\ref{rm:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands. It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding equivalent channel and active precoder are also optimal for the whole \gls{r-e} region. Hence, the achievable \gls{r-e} region is obtained by optimizing the waveform amplitude and splitting ratio. On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal \gls{ris} reflection coefficient varies at different \gls{r-e} trade-offs points for broadband \gls{swipt}. As shown in Fig.~\ref{fg:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high \gls{snr}, or focused on a few strongest subbands to boost the output \gls{dc}, thanks to adaptive passive beamforming.
		\end{subsubsection}

### 2024-03-30 content/chapter_4.tex
:triangular_flag_on_post: Initial submission 240330

		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
		\begin{figure}[H]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_4/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_4/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer corresponds to state \num{2}.
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
			\label{re:dynamic_passive_beamforming}
		\end{remark}

@@

		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
		The backscatter symbol $x_k$ (resp. symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp. value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp. $p(x_{m_{\mathcal{K}}})$).
		\begin{remark}
			Dispersed RIScatter nodes encode independently such that
			\begin{equation}
				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
				\label{eq:equivalent_distribution}
			\end{equation}
			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
			\label{re:independent_encoding}
		\end{remark}

@@

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}

@@

		\begin{remark}
			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
			\label{re:input_kkt_distribution}
		\end{remark}
	\end{subsection}

@@

		\begin{remark}
			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
			\label{re:backscatter_decision}
		\end{remark}

		\begin{remark}
			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
			\label{re:augmented_source}
		\end{remark}

		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
		\begin{maxi!}
			{\scriptstyle{\mathbf{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		whose global optimal solution has been obtained in recent works.
		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T}){-}L)\bigr)$.
		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
		\begin{equation}
			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_ml}
		\end{equation}
		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

@@

			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}

>>>>

		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
		\begin{figure}[H]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_4/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_4/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer corresponds to state \num{2}.
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
			\label{rm:dynamic_passive_beamforming}
		\end{remark}

@@

		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
		The backscatter symbol $x_k$ (resp. symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp. value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp. $p(x_{m_{\mathcal{K}}})$).
		\begin{remark}
			Dispersed RIScatter nodes encode independently such that
			\begin{equation}
				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
				\label{eq:equivalent_distribution}
			\end{equation}
			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
			\label{rm:independent_encoding}
		\end{remark}

@@

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{rm:non_gaussian}
		\end{remark}

@@

		\begin{remark}
			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
			\label{rm:input_kkt_distribution}
		\end{remark}
	\end{subsection}

@@

		\begin{remark}
			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
			\label{rm:backscatter_decision}
		\end{remark}

		\begin{remark}
			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
			\label{rm:augmented_source}
		\end{remark}

		Thanks to Remark \ref{rm:backscatter_decision} and \ref{rm:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
		\begin{maxi!}
			{\scriptstyle{\mathbf{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		whose global optimal solution has been obtained in recent works.
		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T}){-}L)\bigr)$.
		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
		\begin{equation}
			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_ml}
		\end{equation}
		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

@@

			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
			This confirms Remark \ref{rm:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}
